%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Teaching Assistants for Data Science} % Job title
    {University of Information Technology} % Organization
    {Ho Chi Minh City, Vietnam} % Location
    {Sep. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped to design course materials and structure for Machine Learning, Deep Learning, and Social Mining course.}
        \item {Supported students in the course with their research projects involving applied Machine Learning, Deep Learning.}
        \item {Developed homework assignments and illustrations for the course's teaching sessions.}
        \item {Collaborated with the lecturer and three other TAs to lead presentations, evaluate coursework, and answer questions from 100+ students.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Research and Development Engineer} % Job title
    {AISIA Research Lab} % Organization
    {Ho Chi Minh City, Vietnam} % Location
    {Oct. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item {Constructed an end-to-end framework for automatically collecting real estate advertisement posts from different data sources.}
        \item {Built fully automated data pipelines on AirFlow for containerized applications using Docker, AWS and Redshift.}
        \item {Designed an overall service architecture and pipelines of the Machine Learning based Noise Detection and Post Type Classification API product.}
        \item {Deployed several API in Python and in the AWS resources.}
        \item {Implemented Superset for analytic dashboards to visualize the results and serve for further analysis and management processes.}
        \item {Analyzed data from an investment fund and related issues; surveyed and implemented solutions based on optimization and statistical models.}
        \item {Utilized python to implement several Machine learning techniques for VDI - A reliable framework for breakthrough in Investment Performance.}
        \item {Conduct various investigations of state-of-the-art ML approaches and develop appropriate models for aspect detection for telesales calls.}
        \item {Extract words, phrases, and sentences that frequently result in successful calls for customers of particular demographics.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
