%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% %---------------------------------------------------------
%   \cventry
%     {Founder \& Writer} % Role
%     {A Guide for Developers in Start-up} % Title
%     {Facebook Page} % Location
%     {Jan. 2015 - PRESENT} % Date(s)
%     {
%       \begin{cvitems} % Description(s)
%         \item {Drafted daily news for developers in Korea about IT technologies, issues about start-up.}
%       \end{cvitems}
%     }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventryp
    {Journal Papers} % Title
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Khanh Quoc Tran}, An T Nguyen, Phu Gia Hoang, Canh Duc Luu, Trong-Hop Do, and Kiet Van Nguyen. 2022. \href{https://doi.org/10.1007/s00521-022-07745-w}{\textbf{Vietnamese Hate and Offensive Detection using PhoBERT-CNN and Social Media Streaming Data}}. Neural Computing and Applications.\qonetag{\textcolor{white}{\textsf\bfseries Q1}} \blogtag{\bfseries SCIE} \blogtag{IF: \bfseries 5.102}} 
        \item {Binh T Nguyen, Tung Tran Nguyen Doan, Son Thanh Huynh, \textbf{Khanh Quoc Tran}, An Trong Nguyen, An Tran-Hoai Le, Anh Minh Tran, Nhi Ho, Trung T Nguyen, and Dang T Huynh. 2022. \href{https://doi.org/10.1109/ACCESS.2022.3195496}{\textbf{An end-to-end named entity recognition platform for Vietnamese real estate advertisement posts and analytical applications}}. IEEE Access, 10:87681–87697. \qonetag{\textcolor{white}{\textsf\bfseries Q1}} \blogtag{\bfseries SCIE} \blogtag{IF: \bfseries 3.476}}
      \end{cvitems}
    }
    
  \cventryp
    {Conference Papers} % Title
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Khanh Quoc Tran}, An Tran-Hoai Le, An Trong Nguyen, Tung Tran Nguyen Doan, Son Huynh Thanh, Bao Le Hoang, Hoang Nguyen Minh, Triet Minh Thai, Hoang Le Huy, Dang T. Huynh, Binh T. Nguyen, Nhi Y. T. Ho and Trung T. Nguyen. 2022. \href{https://aclanthology.org/2021.paclic-1.72}{\textbf{SEND: A Simple and Efficient Noise Detection Algorithm for Vietnamese Real Estate Posts}}. In Proceedings of the 36th Pacific Asia Conference on Language, Information and Computation. \qtwotag{\textcolor{white}{\textsf\bfseries Rank B}} \blogtag{\bfseries CORE2021}}
        \item {\textbf{Khanh Quoc Tran}, An Trong Nguyen, An Tran-Hoai Le, and Kiet Van Nguyen. 2021. \href{https://aclanthology.org/2021.paclic-1.72}{\textbf{ViVQA: Vietnamese Visual Question Answering}}. In Proceedings of the 35th Pacific Asia Conference on Language, Information and Computation, pages 546–554. \qtwotag{\textcolor{white}{\textsf\bfseries Rank B}} \blogtag{\bfseries CORE2021}}
      \end{cvitems}
    }

    \cventryp
    {} % Title
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Khanh Quoc Tran}, Khanh Quoc Tran, Phap Ngoc Trinh, Khoa Nguyen-Anh Tran, An Tran-Hoai Le, Luan Van Ha, and Kiet Van Nguyen. 2021. \href{https://doi.org/10.3233/faia210036}{\textbf{An Empirical Investigation of Online News Classification on an Open-Domain, Large-Scale and High-Quality Dataset in Vietnamese}}. In New Trends in Intelligent Software Methodologies, Tools and Techniques, pages 367–379. IOS Press \qthreetag{\textcolor{white}{\textsf\bfseries Rank C}} \blogtag{\bfseries CORE2021}}
        \item {\textbf{Khanh Quoc Tran}, Binh Van Duong, Linh Quang Tran, An Le-Hoai Tran, An Trong Nguyen, and Kiet Van Nguyen. 2021. \href{https://doi.org/10.1007/978-3-030-79463-7_48}{\textbf{Machine Learning-Based Empirical Investigation for Credit Scoring in Vietnam’s Banking}}. In International Conference on Industrial, Engineering and Other Applications of Applied Intelligent Systems, pages 564–574. Springer. \qthreetag{\textcolor{white}{\textsf\bfseries Rank C}} \blogtag{\bfseries CORE2021}}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
